Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-21 latex/article.tex
hop

To implement the integration on $B_R(\vx)\cap\Shape$\todo{Check ball
  radii w.r.t. notations in sect2)
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
to estimate the geometrical moment as the sum of the geometrical
moments of each elementary cubes lying in the intersection. On GPU,
\emph{mipmap} textures to obtain a multiresolution information: if the
input binary object is stored in a 3D texture, GPU hardware can
construct a multiresolution pyramid such that 8 neighboring voxel
intensities at level $l$ are averaged to define the voxel value at
level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$
belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
consequence, we can approximate the volume of $B_R(x)\cap\Shape$ by
considering mipmap values at a given resolution $l$
(Fig.~\ref{fig:approx}-$c$). In this case, errors only occurs for
cells lying inside $\Shape$ (with density 1) not entirely covered by
$B_R(\vx)$.
\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation from pixel
    counting $(b)$ or from densities (represented by different
    grayvalues) in a mipmap approximation of $\Shape$.}
  \label{fig:approx}
\end{figure}

>>>>

To implement the integration on $B_R(\vx)\cap\Shape$\todo{Check ball
  radii w.r.t. notations in sect2}
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
to estimate the geometrical moment as the sum of the geometrical
moments of each elementary cubes lying in the intersection. On GPU,
\emph{mipmap} textures to obtain a multiresolution information: if the
input binary object is stored in a 3D texture, GPU hardware can
construct a multiresolution pyramid such that 8 neighboring voxel
intensities at level $l$ are averaged to define the voxel value at
level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$
belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
consequence, we can approximate the volume of $B_R(x)\cap\Shape$ by
considering mipmap values at a given resolution $l$
(Fig.~\ref{fig:approx}-$c$). In this case, errors only occurs for
cells lying inside $\Shape$ (with density 1) not entirely covered by
$B_R(\vx)$.
\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation from pixel
    counting $(b)$ or from densities (represented by different
    grayvalues) in a mipmap approximation of $\Shape$.}
  \label{fig:approx}
\end{figure}
